An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-30 VLDB2026/main.tex
1

		%		\caption{Time and space overhead of attribute filtering index construction}
		\caption{\textcolor{violet}{Time and Space Overhead}}
		\label{fig:build_index_comparison}
	\end{figure}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query (Single Thread) }
		\label{fig:exp_1_1_SingleLabel_1thread}
	\end{figure*}

@@

	\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
	\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
	\label{fig:exp_3_1}

@@

		\caption{Different AS under the Same Algorithm}
		\label{fig:exp_5_2_combined}
	\end{figure*}

@@

	% 5. 全局总标题
	\caption{\textcolor{violet}Scalability Study——Attribute}
	\label{fig:TrinityExtension——Attribution_main}
\end{figure*}

@@

		%		\caption{Time and space overhead of range filtering index construction}
%		\caption{Time and space overhead of index construction}
		\caption{\textcolor{violet}{Time and Space Overhead}}
		\label{fig:rangeFilter_build_index_comparison}
	\end{figure}
	\subsection{Range Filtering}
	\textcolor{blue}{Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value. The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones. }
	\subsubsection{\textcolor{violet}{Time and Space overhead.}}

@@

	% 5. 全局总标题
	\caption{\textcolor{violet}Scalability Study——Range}
	\label{fig:TrinityExtension——Attribution_main}
\end{figure*}

>>>>

		%		\caption{Time and space overhead of attribute filtering index construction}
		\caption{\textcolor{violet}{Time and Space Overhead (Attribute Filtering)}}
		\label{fig:build_index_comparison}
	\end{figure}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query }
		\label{fig:exp_1_1_SingleLabel_1thread}
	\end{figure*}

@@

	\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
	\caption{
		 \centering
		Effect of Attribute Distribution on Query Performance \\
		(Strong: robust to attribute distribution shifts; Weak: sensitive to attribute distribution shifts.)}

	\label{fig:exp_3_1}

@@

		\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
		\label{fig:exp_5_2_combined}
	\end{figure*}

@@

	% 5. 全局总标题
	\caption{\textcolor{violet}Scalability Study (Attribute Filtering)}
	\label{fig:TrinityExtension——Attribution_main}
\end{figure*}

@@

		%		\caption{Time and space overhead of range filtering index construction}
%		\caption{Time and space overhead of index construction}
		\caption{\textcolor{violet}{Time and Space Overhead (Range Filtering)}}
		\label{fig:rangeFilter_build_index_comparison}
	\end{figure}
	\subsection{Range Filtering}
	\textcolor{blue}{Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value. The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones. }
	\subsubsection{\textcolor{violet}{Time and Space overhead.}}

@@

	% 5. 全局总标题
	\caption{\textcolor{violet}Scalability Study (Range Filtering)}
	\label{fig:TrinityExtension——Attribution_main}
\end{figure*}
